### 2021-09-03 presentation/presentation.tex
add flowchart

\usepackage[english]{babel}
% or whatever

@@

    Coordinator updates allocation~\eqref{eq:thetaNegot} using adequate versions of $\vec{\lambda}_{i}$ for each agent: $\vec{\lambda}_{i}^{\star}(\vec{\theta}\p)$, if $d_{i}=0$ and ${\vec{\lambda}_{i}}_{\mathrm{rec}}$, if ${d_{i}=1}$\;
    $p:=p+1$
  }}
    \caption{Secure DMPC.}\label{alg:safeDMPC}
  \end{algorithm}
  }
\end{frame}

\begin{frame}
  \begin{figure}[!t]
    \centering
    % inkscape -Dz flowchartAlg2.svg --export-latex -AflowchartAlg2.pdf
    % \footnotesize
    \def\svgwidth{.4\textwidth} \input{../img/flowchartAlg2.pdf_tex}
    \caption{Scheme of DMPC using a \emph{coordinator} and $M$ agents.}\label{fig:schemeQuantity}
  \end{figure}
\end{frame}

>>>>

\usepackage[english]{babel}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,positioning}
\usetikzlibrary{overlay-beamer-styles}
% or whatever

@@

    Coordinator updates allocation~\eqref{eq:thetaNegot} using adequate versions of $\vec{\lambda}_{i}$ for each agent: $\vec{\lambda}_{i}^{\star}(\vec{\theta}\p)$, if $d_{i}=0$ and ${\vec{\lambda}_{i}}_{\mathrm{rec}}$, if ${d_{i}=1}$\;
    $p:=p+1$
  }}
    \caption{Secure DMPC.}\label{alg:safeDMPC}
  \end{algorithm}
  }

\end{frame}

\begin{frame}
  \begin{figure}[h]
    \centering
  \scalebox{.6}{
    \begin{tikzpicture}[font=\small,thick,node distance=.6cm and 6cm]
      \draw[loosely dashed,
      minimum width=2.5cm,
      minimum height=1cm] (8cm,1cm) -- (8cm,-10cm);

      \node[] at (5cm,0cm) {\Large Detection Phase};
      \node[] at (11cm,0cm) {\Large Negotiation Phase};

      \node[draw,
      rounded rectangle,
      fill=gray!90!black!50,
      alt=<{2}>{fill=supelecRed!90,text=white},
      minimum width=2.5cm,
      minimum height=1cm] (block1) {Start};

      \node[draw,
      trapezium,
      trapezium left angle = 65,
      trapezium right angle = 115,
      trapezium stretches,
      align=center,
      fill=supelecRed!10,
      alt=<{3}>{fill=supelecRed!90,text=white},
      below=of block1,
      minimum width=3.5cm,
      minimum height=1cm
      ] (block2) { Coordinator sends \\random $\vec{\theta}_{i}^{(h)}$};

      \node[draw,
      trapezium,
      trapezium left angle = 65,
      trapezium right angle = 115,
      trapezium stretches,
      align=center,
      fill=supelecRed!10,
      alt=<{4}>{fill=supelecRed!90,text=white},
      below=of block2,
      minimum width=3.5cm,
      minimum height=1cm
      ] (block3) { Agents send \\ $\vec{\lambda}_{i}^{(h)}(\vec{\theta}_{i}^{(h)})$};

      \node[draw,
      trapezium,
      trapezium left angle = 65,
      trapezium right angle = 115,
      trapezium stretches,
      align=center,
      below=of block3,
      fill=supelecRed!10,
      alt=<{5}>{fill=supelecRed!90,text=white},
      minimum width=3.5cm,
      minimum height=1cm
      ] (block4) { Coordinator estimate parameters};

      \node[draw,
      diamond,
      below=of block4,
      minimum width=2.5cm,
      fill=supelecRed!50,
      alt=<{6}>{fill=supelecRed!90,text=white},
      align=center,
      inner sep=0] (block5) { Estimates\\ converge?};

      \node[draw,
      trapezium,
      trapezium left angle = 65,
      trapezium right angle = 115,
      trapezium stretches,
      align=center,
      fill=supelecRed!10,
      alt=<{7}>{fill=supelecRed!90,text=white},
      right=1cm of block5,
      minimum width=3.5cm,
      minimum height=1cm
      ] (block6) { Coordinator detects \\selfish agents};

      \node[coordinate,right=6.cm of block2] (block12) {};

      \node[draw,
      trapezium,
      trapezium left angle = 65,
      trapezium right angle = 115,
      trapezium stretches,
      align=center,
      right=of block12,
      fill=supelecRed!10,
      alt=<{8}>{fill=supelecRed!90,text=white},
      minimum width=3.5cm,
      minimum height=1cm
      ] (block7) { Coordinator sends \\$\vec{\theta}_i^{(h)}$};
      \node[draw,
      trapezium,
      trapezium left angle = 65,
      trapezium right angle = 115,
      trapezium stretches,
      align=center,
      fill=supelecRed!10,
      alt=<{9}>{fill=supelecRed!90,text=white},
      below=of block7,
      minimum width=3.5cm,
      minimum height=1cm
      ] (block8) { Agents send \\$\vec{\lambda}_i(\vec{\theta}_{i}^{(h)})$};

      \node[draw,
      trapezium,
      trapezium left angle = 65,
      trapezium right angle = 115,
      trapezium stretches,
      align=center,
      fill=supelecRed!10,
      alt=<{10}>{fill=supelecRed!90,text=white},
      below=of block8,
      minimum width=3.5cm,
      minimum height=1cm
      ] (block9) { Coordinator updates \\allocation accordingly};

      \node[draw,
      diamond,
      below=of block9,
      minimum width=2.5cm,
      fill=supelecRed!50,
      alt=<{11}>{fill=supelecRed!90,text=white},
      align=center,
      inner sep=0] (block10) { Negotiation\\ converges?};

      \node[draw,
      rounded rectangle,
      below=of block10,
      fill=gray!90!black!50,
      alt=<{12}>{fill=supelecRed!90,text=white},
      minimum width=2.5cm,
      minimum height=1cm,] (block11) { Apply first control};

      \draw[-latex] (block1) edge (block2)
      (block2) edge (block3)
      (block3) edge (block4)
      (block4) edge (block5);

      \draw[-latex] (block7) edge (block8)
      (block8) edge (block9)
      (block9) edge (block10);

      \draw[-latex] (block5) -- (block6)
      node[pos=0.4,fill=white,inner sep=0]{Yes};

      \draw[-latex] (block10) -- (block11)
      node[pos=0.4,fill=white,inner sep=0]{Yes};

      \draw[-latex] (block6) -| ($(block7.west) - (3cm,0)$) -- (block7.west);

      \draw[-latex] (block10) -| ($(block7.east) + (1.5cm,0)$)
      node[pos=0.25,fill=white,inner sep=0]{No} -- (block7.east);

      \draw[-latex] (block5) -| ($(block2.west) - (1.5cm,0)$)
      node[pos=0.25,fill=white,inner sep=0]{No} -- (block2.west);
    \end{tikzpicture}
    }
    \caption{Scheme of DMPC using a \emph{coordinator} and $M$ agents.}\label{fig:schemeQuantity}
  \end{figure}
\end{frame}
